---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
library(devtools)
```

# `qualR` - package review

## **Reviewer:** [\@beatrizmilz](https://github.com/beatrizmilz)

### Review Submitted: ....

<br>

This report contains documents associated with the review of **rOpenSci** submitted package:

### **`qualR`: ropensci/software-review**  issue [\#474](https://github.com/ropensci/software-review/issues/474).

<br>

## Package info

**Description:**

A package to download information from CETESB QUALAR and
    MonitorAr systems. It contains function to download different parameters, a set of
    criteria pollutants and the most frequent meteorological parameters used in
    air quality data analysis and air quality model evaluation.

**Author:** `r c(
    person(given = "Mario",
           family = "Gavidia-Calderón",
           role = c("aut", "cre"),
           email = "mario.calderon@iag.usp.br",
           comment = c(ORCID = "0000-0002-7371-1116")),
    person(given = "Maria de Fatima",
           family = "Andrade",
           role = c("ctb", "ths"),
           email = "maria.andrade@iag.usp.br",
           comment = c(ORCID = "0000-0001-5351-8311")),
    person(given = "Daniel",
           family = "Schuch",
           role = c("aut","ctb"),
           email = "d.schuch@northeastern.edu",
           comment = c(ORCID = "0000-0001-5977-4519")))`

**repo url:** <https://github.com/quishqa/qualR>

**website url:** <https://quishqa.github.io/qualR/>

## Review info


#### See [reviewer guidelines](https://ropensci.github.io/dev_guide/reviewerguide.html) for further information on the rOpenSci review process.

**key review checks:**

- Does the code comply with **general principles in the [Mozilla reviewing guide](https://mozillascience.github.io/codeReview/review.html)**?
- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
- Are there **improvements** that could be made to the **code style?**
- Is there **code duplication** in the package that should be reduced?
- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?
- Is the [**documentation**](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) **clear and sufficient**?

Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://ropensci.github.io/dev_guide/policies.html#code-of-conduct) is mandatory for everyone involved in our review process.



### session info


```{r sessionInfo, echo=TRUE}
sessionInfo()
```


```{r pkg_dir, echo=TRUE}
pkg_dir <- "/home/bea/GitHub/ropensci_reviews/qualR"
pkg_dir
```

## Test installation

### test local `qualR` install:

```{r test-local, eval=FALSE, include=TRUE}
install(pkg_dir, dependencies = T, build_vignettes = T)
```

```{r github-rm, eval=FALSE, include=TRUE}
remove.packages("qualR")
```


#### **comments:**

The local installation worked. ✨

***

### test install of `qualR` from GitHub with:

```{r test-github, eval=FALSE, include=TRUE}
devtools::install_github("quishqa/qualR", dependencies = T, build_vignettes = T)
```

#### **comments:**

 The installation via GitHub worked. ✨


## Check package integrity

### run checks on `qualR` source:

```{r check-checks, eval=FALSE, include=TRUE}
devtools::check(pkg_dir)
```


**Check results:** 

```
── R CMD check results ─────────────────────────────── qualR 0.9.5 ────
Duration: 1m 54s

> checking R/sysdata.rda ... OK
   WARNING
  ‘qpdf’ is needed for checks on size reduction of PDFs

> checking top-level files ... NOTE
  Non-standard files/directories found at top level:
    ‘CONTRIBUTING.md’ ‘LICENSE.md’ ‘README.Rmd’ ‘_pkgdown.yml’
    ‘appveyor.yml’ ‘codecov.yml’ ‘codemeta.json’ ‘data-raw’ ‘docs’
    ‘paper.bib’ ‘paper.md’ ‘pin_nox_lock20.png’ ‘rj_centro_2019.png’
    ‘usp_o3_aug21.png’

0 errors ✓ | 1 warning x | 1 note x
```


#### **comments:**

The check returned 1 note and 1 warning.

About the warning:

The warning of qpdf is related to an external program. In this Stackoverflow answer there is an explanation for it: https://stackoverflow.com/a/44649267


About the note:

There are some files that are not needed to the package be build, so it needs to be ignored on `.Rbuildignore` . One way to do that is to use `usethis::use_build_ignore("relative_path_to_the_file)`. But I do not recommend to use this function to all the files that the Check listed. There are some files that would be better located in other directories, not in the root of the package (such as the images and the files related to the paper being written about the package).  In this link, there is more information about the `.Rbuildignore` file: https://r-pkgs.org/package-structure-state.html#rbuildignore  
Ex:

```
> usethis::use_build_ignore("CONTRIBUTING.md")
✓ Setting active project to '/home/bea/GitHub/ropensci_reviews/qualR'
✓ Adding '^CONTRIBUTING\\.md$' to '.Rbuildignore'
```

***

### run tests on `qualR` source:

```{r check-tests, eval=FALSE, include=TRUE}
devtools::test(pkg_dir)
```


**Tests results:** 

```
══ Results ════════════════════════════════════════════════════════════
Duration: 71.1 s

[ FAIL 0 | WARN 0 | SKIP 0 | PASS 8 ]
```


#### **comments:**

All the tests passed. There are only a few tests. I recommend the authors to write more expectations with `expect_*()`.



***


### check `qualR` for goodpractice:

```{r test-goodpractice, eval=FALSE, include=TRUE}
goodpractice::gp(pkg_dir)
```

```
── GP qualR ───────────────────────────────────────────────────────────

It is good practice to

  ✖ avoid calling setwd(), it changes the global
    environment. If you need it, consider using on.exit() to
    restore the working directory.

    tests/testthat/test-CetesbRetrieveParam.R:4:11
    tests/testthat/test-CetesbRetrieveParam.R:9:3
    tests/testthat/test-MonitorArRetrieve.R:4:11
    tests/testthat/test-MonitorArRetrieve.R:7:3

  ✖ fix this R CMD check NOTE: Note: found 40 marked
    UTF-8 strings
  ✖ fix this R CMD check WARNING: LaTeX errors when
    creating PDF version. This typically indicates Rd
    problems.
  ✖ fix this R CMD check ERROR: Re-running with no
    redirection of stdout/stderr. Hmm ... looks like a package
    Warning in texi2dvi(file = file, pdf = TRUE, clean =
    clean, quiet = quiet, : texi2dvi script/program not
    available, using emulation Error in texi2dvi(file = file,
    pdf = TRUE, clean = clean, quiet = quiet, : pdflatex is
    not available Warning in texi2dvi(file = file, pdf = TRUE,
    clean = clean, quiet = quiet, : texi2dvi script/program
    not available, using emulation Error in texi2dvi(file =
    file, pdf = TRUE, clean = clean, quiet = quiet, : pdflatex
    is not available Error in running tools::texi2pdf() You
    may want to clean up by 'rm -Rf
    /tmp/RtmpNm3vzd/Rd2pdf3bab53f279cd'
```




#### **comments:**

<!-- record comments on goodpractice here -->

***

## Check package metadata files

### inspect

- #### [README](https://github.com/quishqa/qualR)
- #### [DESCRIPTION](https://github.com/quishqa/qualR/blob/master/DESCRIPTION)
- #### [NAMESPACE](https://github.com/quishqa/qualR/blob/master/NAMESPACE)

### spell check

```{r spell-check, eval=FALSE, include=TRUE}
devtools::spell_check(pkg_dir)
```

#### **comments:**

<!-- record comments on metadata files here -->

***

## Check documentation

online documentation: **<https://quishqa.github.io/qualR/>**

* Is the [documentation](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) clear and sufficient?

### test `qualR` function help files:

```{r test-help, eval=FALSE, include=TRUE}
help(package = "qualR")
```

#### **comments:**

<!-- record comments on help files here -->

***

### test `qualR` vignettes:

```{r test-vignettes, eval=FALSE, include=TRUE}
vignette(package = "qualR")
```

#### **comments:**

<!-- record comments on vignettes here -->

***

## Test functionality:

- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?

```{r free-style, eval=FALSE, include=TRUE}
library("qualR")
```

```{r parse-functions, eval=FALSE, include=TRUE}
exports <-ls("package:qualR")
exports
```

<!-- experiment with package functions -->

```{r exp-chunk}


```

#### **comments:**

<!-- record comments on package experimentation here -->

***

## Inspect code:

- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
    * good [function & variable naming?](https://ropensci.github.io/dev_guide/building.html#function-and-argument-naming)
    * good [dependency management](https://ropensci.github.io/dev_guide/building.html#package-dependencies)?
- Are there **improvements** that could be made to the [**code style?**](https://ropensci.github.io/dev_guide/building.html#code-style)
- Is there **code duplication** in the package that should be reduced?

```{r inspect-code, eval=FALSE, include=TRUE}
pkgreviewr::pkgreview_print_source("qualR")
```
**\* might not be suitable for large packages with many exported functions**


<br>
<br>

#### **comments:**

<!-- record comments on package source code here -->


## Review test suite:

See guidance on [testing](https://ropensci.github.io/dev_guide/building.html#testing) for further details.

### test coverage

```{r pkg_coverage, eval=FALSE, include=TRUE}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://github.com/quishqa/qualR/blob/master/tests/testthat)


#### **comments:**

<!-- record comments on testing suite here -->


***
